### 2022-03-03 ms/PrestigeBias.tex
update

\paragraph{Success bias.} \citet[Ch.8, p.247-249]{evolutionBook} describe a method of inheritance using a \textit{blend}, i.e weighted average of the trait of the entire generation. They define $F$ as a weighted average  of the role-models' traits in a single generation:
\begin{equation}
F_i(\vec{X}) = \sum_{j=1}^N \Big(G_{ij}\cdot X_{ij}\Big) \\\\
\end{equation}
where $G_{i,j}$ is: 
\begin{equation}
G_{ij} = \frac{\beta(A_{ij})}{\sum_{l=1}^{N} \beta(A_{il})}
\end{equation}
We define $G_{ij}$ to be the \textit{Success bias} of role-model $j$ in the eyes of copier $i$.
$A_{i,j}$ is the absolute indicator trait value copier $i$ estimates role-model $j$ has:
\begin{equation}\label{eq:relativeIndicator}
A_{i,j} = A_j + e_i,
\end{equation}
where $e_i$ is the copier's error of estimation, $\vec{e} \sim N(0,\frac{1}{\eta^2})$.
$\beta(X)$ is the bias function, meant to quantify the success bias of a role-model:
\begin{equation}\label{eq:success_bias}
\beta(A_{i,j}) = b \cdot \exp^{\Big(-\frac{(A_{i,j} - \hat{A})^2}{2J}\Big)},
\end{equation} 
where $\hat{A}$ is the optimal indicator value and $J,b$ are model parameters to control the "strength" of the bias.
$G_{i,j}$ is therefore the relative success score copier $i$ assigns to role-model $j$, resembling \textit{relative fitness} in genetic transmission models.

@@

\subsection{Dirichlet-Multinomial Distribution Approximation}
\paragraph{Reminder: \textit{Pólya urn model}}  is a stochastic process that is defined as such: 
The process consists of $N$ draws from an urn with an initial amount of colored balls of $M$ colors. When a ball is drawn, it is then placed back in the urn together with an additional new ball of the same colour.\\
Let $\vec{U_i} = \{u_{i,1},u_{i,2},...,u_{i,M}\}$  where $u_{i,j}$ is the number of balls of the $j$-th color in the urn after $i$ draws.
Let $S_{i,j}=1$ when drawing a $j$ colored ball on the $i$-th draw, and $0$ otherwise. The probability that $S_{i,j}=1$ given $\vec{U_{i-1}}$ is:
\begin{equation}\label{polya}
\begin{split}
P(S_{i,j} = 1 | \vec{U_{i-1}}) & = \frac{u_{i-1,j}}{\sum\limits_{m=1}^{M} u_{i-1,m}} = \frac{o_j + w_{i-1,j}}{\sum\limits_{m=1}^{M} o_m + w_{i-1,m}}\\\\
 & = \frac{o_j + w_{i-1,j}}{i-1 + \sum\limits_{m=1}^{M} o_m}
\end{split}
\end{equation}
where $o_j$ is the initial number of balls of the colour $j$ in the urn, and $w_{i,j}$ is the number of new balls that were added to the urn after $i$ draws of the color $j$.

\paragraph{Proposition:} process $\big\{\vec{K}_i\big\}_{i=1}^N$ is equivalent to a \textit{Pólya urn model} when $e=e_i=e_j$ and $\alpha=\alpha_j=\alpha_i$ for all $i,j \in N$.
\paragraph{Proof:} 
We denote $\alpha'$ as the odds ratio between the weights of the indicator and the influence ($\alpha'=\frac{\alpha}{1-\alpha}$). 
Using \cref{prestige_eq} we get:
\begin{equation}\label{copier_choose}
\begin{split}
G_{i,j} & = \frac{\alpha\cdot \beta(A'_j) + (1-\alpha) \cdot K_{i-1,j}}{W_i} \cdot \frac{1-\alpha}{1-\alpha} \\\\
&= \frac{\alpha'\beta(A'_j) + K_{i-1,j}}{\sum\limits_{m=1}^{N} \alpha'\beta(A'_m) + K_{i-1,m}}\\\\
& =\frac{\alpha'\beta(A'_j) + K_{i-1,j}}{i-1 + \sum\limits_{m=1}^{N} \alpha'\beta(A'_m)}
\end{split}
\end{equation}
We see that \cref{polya} and \cref{copier_choose} are equivalent when setting $M=N$, $o_j = \alpha'\beta(A'_j)$, $w_{i,j} = K_{i,j}$, completing the proof.

@@

\paragraph{Numeric validation:} We showed our process is DM (Dirichlet-Multinomial) distributed when there are no errors when copying or evaluating the traits, and when $\alpha$ is homogeneous in the population. To test if our process is still DM distributed when there are copying errors in the population, we ran 400 simulations for three different error scales ($\eta$). To check the resemblance of the DM approximation to the original iterative process, we measure the $\chi^2$ statistic of both processes and the results can be seen in \cref{fig:chiSquaredHist}.
Even with a relatively high error scales (1\% and 10\% of J) we can see the distributions of the $\chi^2$ metrics are very similar.
With a higher $\eta$ (e.g $\eta=J$), which is approximately 100\% error when evaluating a trait, the distributions are noticeably different.

In addition to the chi-squared test, we want to observe how well does the Dirichlet-Multinomial distribution approximates our entire model, and not just one generation in it.
To do that we simplify our model to a binary model, so the simulations of the model to run in a feasible amount of time.

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.3\textwidth}
  \subcaption{Error scale is 0.01}
    \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_0_01.pdf}
    \end{subfigure}
    \begin{subfigure}[a]{0.3\textwidth}
    \subcaption{Error scale is 0.1}
    \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_0_1.pdf} 
    \end{subfigure}
    \begin{subfigure}[a]{0.3\textwidth}
     \subcaption{Error scale is 1(=J)}
    \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_J.pdf}
  \end{subfigure}
  \caption{Demonstrates the similarities between the $\chi ^2$ metric of 	           the DM approximation and the full model, showing the approximation is good until a very high error rate. Population size $N=2000$. 400 simulations per figure}	
  \label{fig:chiSquaredHist}
  \end{center}
\end{figure}

@@

The expected number of individuals of a DM distribution is:
\begin{equation}
E[X'] = N  \frac{\alpha_1}{\alpha_1+\alpha_2},
\end{equation}
where $\alpha_1 = \alpha' X$ and $\alpha_2 = \alpha'(N-X)\beta$, from  \cref{eq:binary-model}.
We want to use frequencies instead of quantities to follow Durret's process so:
\begin{equation}
E[x'] = E[\frac{X'}{N}] = \frac{1}{N}E[X']
\end{equation}
Putting it together we get:
\begin{equation}
\begin{split}
E[x'] &= \frac{1}{N}N\frac{\alpha' xN}{\alpha' xN + \alpha' N (1-x)\beta}\\\\
	 &= \frac{x}{x + (1-x)\beta}
\end{split}
\end{equation}

@@

Again following Durret we want to calculate:
\begin{equation}
V(x'-x) = V(x') - V(x) \approx  x(1-x)(\frac{1 + \alpha'}{1 + \alpha' N})
\end{equation}
because $x$ is a constant so $V(x) = 0$

In our model, $\alpha'$ is the odds ratio of a parameter we called "indicator weight", denoted in our model as $\alpha$, so:
\begin{equation}
\alpha' = \frac{\alpha}{1-\alpha}
\end{equation}

And combining with the previous equations we get:
\begin{equation}\label{eq:const_var}
\begin{split}
V(x'-x) & \approx x(1-x)(\frac{1 + \frac{\alpha}{1-\alpha}}{1 + \frac{\alpha}{1-\alpha} N})\\\\
 &= x(1-x)(\frac{\frac{1-\alpha+\alpha}{1-\alpha}}{\frac{1-\alpha+\alpha N}{1-\alpha}})\\\\
 &= x(1-x)(\frac{1}{1- \alpha(1-N)})\\\\
  &= x(1-x)(\frac{1}{\alpha N + (1-\alpha)})\\\\
  &= x(1-x)\frac{1}{N_e}
\end{split}
\end{equation}

@@

The proof is based on the proof of \citet{changeEnv}, proving a similar scenario.
\paragraph{Proof by induction:}
From \cref{eq:expec_freq} we know that
\begin{equation}\label{eq:ch_1}
\begin{split}
E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\bigg|X_t\right] &= \frac{X_t}{N}\left(1-\frac{X_t}{N}\right)(1-\beta_{t+1}) \\\\
&= \frac{1}{N}\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)s_{t+1}
\end{split}
\end{equation}
Also note that using the definition of $V(y)=E[y^2]-(E[y])^2$
\begin{equation}
\begin{split}
E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] &= E\left[\frac{X_t}{N}-\left(\frac{X_t}{N}\right)^2\right] \\\\
&= E\left[\frac{X_t}{N}\right]-E\left[\left(\frac{X_t}{N}\right)^2\right] \\\\
&= E\left[\frac{X_t}{N}\right] - V\left(\frac{X_t}{N}\right) - \left(E\left[\frac{X_t}{N}\right]\right)^2
\end{split}
\end{equation}

we can now use the induction assumption of $V(\frac{X_t}{N})$ and get
\begin{equation}
\begin{split}
E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] &\simeq
E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right)-\frac{1}{N_e}tx(1-x)
\end{split}
\end{equation}
From \cref{eq:ch_1} we know that
\begin{equation}
\begin{split}
E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] &= \frac{1}{N}s_{t+1}E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] \\\\
&\simeq \frac{1}{N}s_{t+1}\left(E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) - \frac{1}{N_e}tx(1-x)\right) \\\\
&\simeq \frac{1}{N}s_{t+1}\cdot E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) - \frac{1}{N_e N}s_{t+1}tx(1-x)
\end{split}
\end{equation}
Now we'll omit $O(\frac{1}{Ne\cdot N})$ and get
\begin{equation}\label{eq:ch_2}
E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] \simeq \frac{1}{N}s_{t+1}\cdot E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right)
\end{equation}

We'll now look at the induction assumption to see that
\begin{equation}
E\left[\frac{X_t}{N}-x\right]=E\left[\frac{X_t}{N}\right]-E[x]=E\left[\frac{X_t}{N}\right]-x ,
\end{equation}
so using the assumption we get
\begin{equation}
\begin{split}
E\left[\frac{X_t}{N}\right] &\simeq \frac{1}{N} S_t x(1-x)+x \\
1 - E\left[\frac{X_t}{N}\right] &\simeq 1- \frac{1}{N} S_t x(1-x)+x
\end{split}
\end{equation}
we'll use both expressions in \cref{eq:ch_2} and get
\begin{equation}\label{eq:ch_3}
\begin{split}
E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] &\simeq \frac{1}{N}s_{t+1} \left(\frac{1}{N} S_t x(1-x)+x \right)\left(1- \frac{1}{N} S_t x(1-x)+x \right) \\\\
&\simeq  \frac{1}{N}s_{t+1}\cdot x(1-x)
\end{split}
\end{equation}
after again omitting $O(\frac{1}{N^2})$ parts of the equation.
To conclude our proof, we see that
\begin{equation}
E\left[\frac{X_{t+1}}{N}-x\right] = E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] + E\left[\frac{X_t}{N}-x\right]
\end{equation}
so again using the induction assumption, together with \cref{eq:ch_3} we get
\begin{equation}
\begin{split}
E\left[\frac{X_{t+1}}{N}-x\right] &\simeq \frac{1}{N}s_{t+1}\cdot x(1-x) + \frac{1}{N}S_t\cdot x(1-x) \\
& \simeq \frac{1}{N}x(1-x)(S_t + s_{t+1}) \\
& \simeq \frac{1}{N} S_{t+1} x(1-x)
\end{split}
\end{equation}
which proves the first part of our preposition.

@@

using \cref{eq:ch_1} we see that:
\begin{equation}\label{eq:ch_var1}
\begin{split}
E\left[\frac{X_{t+1}}{N} \bigg|X_t \right] - E\left[\frac{X_{t}}{N} \bigg|X_t \right] &= \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \\\\
E\left[\frac{X_{t+1}}{N} \bigg|X_t \right] = \frac{X_t}{N} &+ \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right)
\end{split}
\end{equation}

@@

\clearpage
\section{Appendix A - Time table}

\paragraph{Today - Oct 2021:}
Find approximation replacing Durrett's equations for the time to fixation.

\paragraph{Nov - Mar 2021:}
Combining the findings to a paper and a thesis.

>>>>

\paragraph{Success bias.} \citet[Ch.8, p.247-249]{evolutionBook} describe a method of inheritance using a \textit{blend}, i.e weighted average of the trait of the entire generation. They define $F$ as a weighted average  of the role-models' traits in a single generation:
\begin{equation}
F_i(\vec{X}) = \sum_{j=1}^N \Big(G_{ij}\cdot X_{ij}\Big) \\
\end{equation}
where $G_{i,j}$ is: 
\begin{equation}
G_{ij} = \frac{\beta(A_{ij})}{\sum_{l=1}^{N} \beta(A_{il})}
\end{equation}
We define $G_{ij}$ to be the \textit{Success bias} of role-model $j$ in the eyes of copier $i$.
$A_{i,j}$ is the absolute indicator trait value copier $i$ estimates role-model $j$ has:
\begin{equation}\label{eq:relativeIndicator}
A_{i,j} = A_j + e_i,
\end{equation}
where $e_i$ is the copier's error of estimation, $\vec{e} \sim N(0,\frac{1}{\eta^2})$.
$\beta(X)$ is the bias function, meant to quantify the success bias of a role-model:
\begin{equation}\label{eq:success_bias}
\beta(A_{i,j}) = b \cdot \exp^{\Big(-\frac{(A_{i,j} - \hat{A})^2}{2J}\Big)},
\end{equation} 
where $\hat{A}$ is the optimal indicator value and $J,b$ are model parameters to control the "strength" of the bias.
$G_{i,j}$ is therefore the relative success score copier $i$ assigns to role-model $j$, resembling \textit{relative fitness} in genetic transmission models.

@@

\subsection{Dirichlet-Multinomial Distribution Approximation}
\paragraph{Reminder: \textit{Pólya urn model}}  is a stochastic process that is defined as such: 
The process consists of $N$ draws from an urn with an initial amount of colored balls of $M$ colors. When a ball is drawn, it is then placed back in the urn together with an additional new ball of the same colour.\\
Let $\vec{U_i} = \{u_{i,1},u_{i,2},...,u_{i,M}\}$  where $u_{i,j}$ is the number of balls of the $j$-th color in the urn after $i$ draws.
Let $S_{i,j}=1$ when drawing a $j$ colored ball on the $i$-th draw, and $0$ otherwise. The probability that $S_{i,j}=1$ given $\vec{U_{i-1}}$ is:
\begin{equation}\label{polya}
\begin{split}
P(S_{i,j} = 1 | \vec{U_{i-1}}) & = \frac{u_{i-1,j}}{\sum\limits_{m=1}^{M} u_{i-1,m}} = \frac{o_j + w_{i-1,j}}{\sum\limits_{m=1}^{M} o_m + w_{i-1,m}}\\
 & = \frac{o_j + w_{i-1,j}}{i-1 + \sum\limits_{m=1}^{M} o_m}
\end{split}
\end{equation}
where $o_j$ is the initial number of balls of the colour $j$ in the urn, and $w_{i,j}$ is the number of new balls that were added to the urn after $i$ draws of the color $j$.

\paragraph{Proposition:} process $\big\{\vec{K}_i\big\}_{i=1}^N$ is equivalent to a \textit{Pólya urn model} when $e=e_i=e_j$ and $\alpha=\alpha_j=\alpha_i$ for all $i,j \in N$.
\paragraph{Proof:} 
We denote $\alpha'$ as the odds ratio between the weights of the indicator and the influence ($\alpha'=\frac{\alpha}{1-\alpha}$). 
Using \cref{prestige_eq} we get:
\begin{equation}\label{copier_choose}
\begin{split}
G_{i,j} & = \frac{\alpha\cdot \beta(A'_j) + (1-\alpha) \cdot K_{i-1,j}}{W_i} \cdot \frac{1-\alpha}{1-\alpha} \\
&= \frac{\alpha'\beta(A'_j) + K_{i-1,j}}{\sum\limits_{m=1}^{N} \alpha'\beta(A'_m) + K_{i-1,m}}\\
& =\frac{\alpha'\beta(A'_j) + K_{i-1,j}}{i-1 + \sum\limits_{m=1}^{N} \alpha'\beta(A'_m)}
\end{split}
\end{equation}
We see that \cref{polya} and \cref{copier_choose} are equivalent when setting $M=N$, $o_j = \alpha'\beta(A'_j)$, $w_{i,j} = K_{i,j}$, completing the proof.

@@

\paragraph{Numeric validation:} We showed our process is DM (Dirichlet-Multinomial) distributed when there are no errors when copying or evaluating the traits, and when $\alpha$ is homogeneous in the population. To support our proof, we tested our approximation empirically using computer simulations.
To test our hypothesis, we used a \textit{goodness of fit} method known as \textit{Pearson's chi-squared test}. In this test, one can reject or accept the null hypothesis, which in our case is the hypothesis that the simulations results were drawn from a DM distribution.

To use this test, we ran many simulations of our original model, and used the mean distribution of copiers. This mean distribution is our observed distribution, and we tested it with the DM expected distribution, using said chi-squared test.
We tested multiple variations of the trait weight parameter ($\alpha$).

In all our tests, the p-value was \textbf{1}. This means that the probability to reject the null hypothesis is essentially nonexistent (the usual threshold for a p-value needed to reject $H_0$ is 0.05 or lower). 
In addition, we found out that for high $\alpha$ values (above 0.5), very few simulations are needed to reach p-value 1. (less than five simulations for $\alpha=0.9$, and less than 20 for $\alpha=0.7$)
For very low $\alpha$ values, which means very high influence weight, the number of simulations needed was 100, which is still a relatively small amount.
To verify our codes results, we also ran the test for different distributions, for example the uniform distribution (all role-models have exactly one copier).

All these tests resulted in a p-value 0, which means we can likely reject $H_0$ for these distributions, as expected.

Once we validated our proof for a single iteration of the model, we went on to more complex validations for the entire model.

@@

The expected number of individuals of a DM distribution is:
\begin{equation}
E[X'] = N  \frac{\alpha_1}{\alpha_1+\alpha_2},
\end{equation}
where $\alpha_1 = \alpha' X$ and $\alpha_2 = \alpha'(N-X)\beta$, from  \cref{eq:binary-model}.
We want to use frequencies instead of quantities to follow Durret's process so:
\begin{equation}
E[x'] = E[\frac{X'}{N}] = \frac{1}{N}E[X']
\end{equation}
Putting it together we get:
\begin{equation}
\begin{split}
E[x'] &= \frac{1}{N}N\frac{\alpha' xN}{\alpha' xN + \alpha' N (1-x)\beta}\\
	 &= \frac{x}{x + (1-x)\beta}
\end{split}
\end{equation}

@@

Again following Durret we want to calculate:
\begin{equation}\label{eq:var_diff_durret}
V(x'-x) = V(x') - V(x) \approx  x(1-x)(\frac{1 + \alpha'}{1 + \alpha' N})
\end{equation}
because $x$ is a constant so $V(x) = 0$

In our model, $\alpha'$ is the odds ratio of a parameter we called "indicator weight", denoted in our model as $\alpha$, so:
\begin{equation}\label{eq:success_ratio}
\alpha' = \frac{\alpha}{1-\alpha}
\end{equation}

Combining \cref{eq:var_diff_durret} and \cref{eq:success_ratio} we get:
\begin{equation}\label{eq:const_var}
\begin{split}
V(x'-x) & \approx x(1-x)(\frac{1 + \frac{\alpha}{1-\alpha}}{1 + \frac{\alpha}{1-\alpha} N})\\
 &= x(1-x)(\frac{\frac{1-\alpha+\alpha}{1-\alpha}}{\frac{1-\alpha+\alpha N}{1-\alpha}})\\
 &= x(1-x)(\frac{1}{1- \alpha(1-N)})\\
  &= x(1-x)(\frac{1}{\alpha N + (1-\alpha)})\\
  &= x(1-x)\frac{1}{N_e}
\end{split}
\end{equation}

@@

The proof is based on the proof of \citet{changeEnv}, proving a similar scenario.
\paragraph{Proof by induction:}
From \cref{eq:expec_freq} we know that
\begin{equation}\label{eq:ch_1}
\begin{split}
E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\bigg|X_t\right] &= \frac{X_t}{N}\left(1-\frac{X_t}{N}\right)(1-\beta_{t+1}) \\
&= \frac{1}{N}\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)s_{t+1}
\end{split}
\end{equation}
Also note that using the definition of $V(y)=E[y^2]-(E[y])^2$
\begin{equation}
\begin{split}
E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] &= E\left[\frac{X_t}{N}-\left(\frac{X_t}{N}\right)^2\right] \\
&= E\left[\frac{X_t}{N}\right]-E\left[\left(\frac{X_t}{N}\right)^2\right] \\
&= E\left[\frac{X_t}{N}\right] - V\left(\frac{X_t}{N}\right) - \left(E\left[\frac{X_t}{N}\right]\right)^2
\end{split}
\end{equation}

we can now use the induction assumption of $V(\frac{X_t}{N})$ and get
\begin{equation}
\begin{split}
E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] &\simeq
E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right)-\frac{1}{N_e}tx(1-x)
\end{split}
\end{equation}
From \cref{eq:ch_1} we know that
\begin{equation}
\begin{split}
E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] &= \frac{1}{N}s_{t+1}E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] \\
&\simeq \frac{1}{N}s_{t+1}\left(E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) - \frac{1}{N_e}tx(1-x)\right) \\
&\simeq \frac{1}{N}s_{t+1}\cdot E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right) - \frac{1}{N_e N}s_{t+1}tx(1-x)
\end{split}
\end{equation}
Now we'll omit $O(\frac{1}{Ne\cdot N})$ and get
\begin{equation}\label{eq:ch_2}
E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] \simeq \frac{1}{N}s_{t+1}\cdot E\left[\frac{X_t}{N}\right]\left(1-E\left[\frac{X_t}{N}\right]\right)
\end{equation}

We'll now look at the induction assumption to see that
\begin{equation}
E\left[\frac{X_t}{N}-x\right]=E\left[\frac{X_t}{N}\right]-E[x]=E\left[\frac{X_t}{N}\right]-x ,
\end{equation}
so using the assumption we get
\begin{equation}
\begin{split}
E\left[\frac{X_t}{N}\right] &\simeq \frac{1}{N} S_t x(1-x)+x \\
1 - E\left[\frac{X_t}{N}\right] &\simeq 1- \frac{1}{N} S_t x(1-x)+x
\end{split}
\end{equation}
we'll use both expressions in \cref{eq:ch_2} and get
\begin{equation}\label{eq:ch_3}
\begin{split}
E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] &\simeq \frac{1}{N}s_{t+1} \left(\frac{1}{N} S_t x(1-x)+x \right)\left(1- \frac{1}{N} S_t x(1-x)+x \right) \\
&\simeq  \frac{1}{N}s_{t+1}\cdot x(1-x)
\end{split}
\end{equation}
after again omitting $O(\frac{1}{N^2})$ parts of the equation.
To conclude our proof, we see that
\begin{equation}
E\left[\frac{X_{t+1}}{N}-x\right] = E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] + E\left[\frac{X_t}{N}-x\right]
\end{equation}
so again using the induction assumption, together with \cref{eq:ch_3} we get
\begin{equation}
\begin{split}
E\left[\frac{X_{t+1}}{N}-x\right] &\simeq \frac{1}{N}s_{t+1}\cdot x(1-x) + \frac{1}{N}S_t\cdot x(1-x) \\
& \simeq \frac{1}{N}x(1-x)(S_t + s_{t+1}) \\
& \simeq \frac{1}{N} S_{t+1} x(1-x)
\end{split}
\end{equation}
which proves the first part of our preposition.

@@

using \cref{eq:ch_1} we see that:
\begin{equation}\label{eq:ch_var1}
\begin{split}
E\left[\frac{X_{t+1}}{N} \bigg|X_t \right] - E\left[\frac{X_{t}}{N} \bigg|X_t \right] &= \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right) \\
E\left[\frac{X_{t+1}}{N} \bigg|X_t \right] = \frac{X_t}{N} &+ \frac{1}{N}s_{t+1}\frac{X_t}{N}\left(1-\frac{X_t}{N} \right)
\end{split}
\end{equation}

@@

\clearpage
\section{Summaries}
\subsection{Animal leadership \citep{animal_leadership}}
There are two main approaches to decision makings of groups in nature: leadership and consensus. Prey leaders would lead the pact when traveling, while other animal group leaders will decide on a nesting site or foraging patches. They found out that leadership is observed mostly when there is a profound social network in the group, and when there are individuals that present leadership behavior. Leaders would usually be high ranking members in the group, such as elders, individuals with many kin relations, or posses other dominant traits. When no individual posses such traits, or when the social network is lacking, a consensus is more likely to occur.
When a leader is present, they will have greater selection costs, such as higher risk for predation, being poisoned by unknown experimental patch, but also greater benefits. For example, given the route to the foraging site was successful, the leader and his closest followers would gain most of the food, unlike in a consensus, where the food would be shared more equally.
It appears leaders appear in simple organisms as well, like fish. In these organisms however, the leader would usually be the hungriest or the weakest, while the rest would prefer to follow, minimizing their costs. In baboons however, \citet{animal_leadership} describe many benefits for the closest associates of the dominant male, such as protection from predators. This is an instance of sexual-selection, where the leader, whose survival chances are lower, gains more sexual partners due to the benefits. ("The greater the risk, the greater the reward")
In humans, leadership also has its perks and costs. Leaders can make decisions that would benefit them and their closest followers the most, while still maintaining group cohesion. However, wrong decision making that would harm the group could result in harm (media, social status, even violent behavior of subjects on certain cases).
In our binary model, we consider a single trait. Consider this trait a trait that would be seen as desirable for a leader. Assuming that, our binary model could be used to predict and explain leader-selection processes, from prom-king to president.
